A Handbook for Tenured Track Faculty in Computer Science in the US

### 2024-08-06 demystify.tex
updates

You should treat the interview as an informal chat. Have ``elevator pitches'' about your research experiences and interests. You might also want to have a 5-minute presentation about your research. If a prof. asks you to read a paper, do it and be prepared to discuss it. You can also ask if you need to prepare for a coding problem. Finally, prepare some thoughtful questions to ask, e.g., about the program, the university, or the professor's research.

@@

\paragraph{Red flags} Various types of red flags can cause concern to the adcom (e.g., too many STEM courses with low or withdraw grades, plagiarism, cheating, or other academic dishonesty). Another one is that you have a history of jumping from one program to another (e.g., you have been in multiple different programs in a short time). Adcom members might have contacts in other programs and heard about your stories, or your LoRs might mention these.

>>>>

You should treat the interview as an informal chat. Have ``elevator pitches'' about your research experiences and interests. You might also want to have a 5-minute presentation about your research. If a prof. asks you to read a paper, do it and be prepared to discuss it. You can also ask if you need to prepare for a coding problem. Finally, prepare some thoughtful questions to ask, e.g., about the program, the university, or the professor's research (see \href{https://github.com/dynaroars/dynaroars.github.io/wiki/Answers-to-Ph.D-Advisor-Guide}{some questions} you can ask a potential adviser).

@@

\paragraph{Red flags} Various types of red flags can cause concern to the adcom (e.g., too many STEM courses with low or withdrawn grades, plagiarism, cheating, or other academic dishonesty). Another one is that you have a history of jumping from one program to another (e.g., you have been in multiple different programs in a short time). Adcom members might have contacts in other programs and heard about your stories, or your LoRs might mention these.

### 2024-08-06 faculty.tex
updates

\section{From a Tenure Evaluation Point of View}
Without a doubt, grants are one of the most, if not the most, important component of tenure evaluation.  The most common reason for not getting tenure is not having enough funding. In an ideal world, research results, e.g., publications, would be the more important; but in reality, funding is often considered more important for tenure evaluation at most R1 universities.
The amount of funding you have is a direct reflection of your research impact and productivity.  It is also a reflection of your ability to write proposals, manage projects, and work with collaborators. More realistically, grants are needed to pay for your students, travel conference, research equipments, and even your own summer salary.

In general, the more funding you have, the better.  However, the quality of the funding is also important.  For example, external NSF grants are more prestigious than an internal grant.  Also, funding from industry, while has a much smaller amount, is often highly competitive, prestigious, and can help show that your research is of interest to industry.  In general, you should aim to get funding from a variety of sources, including NSF, Defense, industry, and internal grants.  This will show that you are able to work with different types of sponsors and that your research is of interest to a wide range of people.

\section{Types of Funding}
\paragraph{NSF} NSF is the obvious funding source for CS. 
Two things stand out for NSF grants: (transparency) proposals are evaluated by an independent panel and are based on merit rather than personal connections; (autonomy) the flexibility and freedom given to focus on pure research without the pressure of producing concrete deliverables.  Because of these reasons, NSF funding is often considered the prestigious and competitive, even for very experienced senior researchers from top places (which don't mean anything). Note that a PI can use at most 2 months of summer salary from NSF grants (if you need the 3rd summer month, you need to find other sources of funding).

@@

However, these sponsors are good sources of funding and can provide the additional resources (e.g., summer months for faculty). Note that some defense programs, e.g., Young Investigator Award, are more like NSF grants, with less stringent requirements and no deliverables required.

@@

\section{Most people suck at grant writing (at first)} Most new assistant professors have no experience in grant writing, and struggle with it in the beginning.  Then eventually they will get used to it and learn to like it (or at least do not hate it as much).  So don't get discouraged.  Keep trying, and you will get better over time.

@@

It's a very different skill than writing research papers.  However, it's a skill that can be learned.  The best way to learn is to read other people's grants, and to write your own.  You will likely get rejected many times, but that's normal.  You will get better over time.  The key is to keep trying, and to not give up.  If you are not getting rejected, you are not aiming high enough.  The best researchers in the world get rejected all the time.  It's part of the process.  So don't get discouraged.  Keep trying, and you will get better over time.

@@

While teaching should take about 40\% of your time and your salary is mainly for teaching, teaching is not as important as research for tenure.  Moreover, for most new faculty, teaching is not as difficult as getting grants. Thus, tenure-track faculty often do not worry much about teaching.

@@

Successfully mentoring students is a key and most rewarding part of your job as a faculty member. 
There will be times when you feel discouraged and frustrated, but there will also be times when you feel proud and happy.  
For tenure you will be expected to mentor undergraduate students and graduate students. You will likely need to graduate at least one PhD student to get tenure.

>>>>

\section{For P\&T}
Without a doubt, grants are one of the most, if not \emph{the} most, important factors in P\&T (or any kind of performance) evaluation.  The most common reason for not getting tenure is not having enough funding. In an ideal world, research results, e.g., publications, would be the more important; but in reality, funding is often considered more important for tenure evaluation at most R1 universities.
The amount of funding you have is a direct reflection of your research impact and productivity.  It is also a reflection of your ability to write proposals, manage projects, and work with collaborators. More realistically, grants are needed to pay for your students, travel conference, research equipments, and even your own summer salary.

In general, the more funding you have, the better.  However, the \emph{quality} of the funding is also important.  For example, external NSF grants are more prestigious than an internal grant because they give more money and are also more competitive.  Also, funding from industry, while has a much smaller amount, is often highly competitive, prestigious, and can help show that your research is of interest to industry.  Finally, you should aim to get funding from a variety of sources, including NSF, Defense, industry, and internal grants.  This will show that you are able to work with different types of sponsors and that your research is of interest to a wide range of people.

\section{Types of Funding}
\paragraph{NSF} NSF is the obvious funding source for CS. 
Two things stand out for NSF grants are (i. \emph{transparency}) proposals are evaluated by an independent panel and are based on merit rather than personal connections, and (ii. \emph{autonomy}) the flexibility and freedom given to focus on pure research without the pressure of producing concrete deliverables.

Because of these reasons, NSF funding is often considered the prestigious and competitive, even for very experienced senior researchers from top places (which don't mean anything). Note that a PI can use at most 2 months of summer salary from NSF grants (if you need the 3rd summer month, you need to find other sources of funding).

@@

However, these sponsors are good sources of funding and can provide the additional resources (e.g., your "3rd" non-NSF summer month). Note that some defense programs, e.g., Young Investigator Award, are more like NSF grants, with less stringent requirements and no deliverables required.

@@

\section{Most people suck at grant writing (at first)} Most new assistant professors have no experience in grant writing, and struggle with it in the beginning.  It becomes especially stressful starting your 3rd year when departmental evaluation starts to give you more pressure and warning if you don't have enough funding. By your midterm or fourth-year review, you are expected to have at least some external funding, and can be in serious trouble if you don't have any. So start early, and don't wait until the last minute to start writing grants.  It's a skill that can be learned, and you will get better over time.  The key is to keep trying, and to not give up.  If you are not getting rejected, you are not aiming high enough.  The best researchers in the world get rejected all the time.  It's part of the process.  So don't get discouraged.  Keep trying, and you will get better over time.

@@

@@

While teaching should take about 40\% of your time (equivalent to research) and your salary is mainly for teaching, teaching is not as nearly as important as research for tenure.  Moreover, for most new faculty, teaching is not as difficult as getting grants or publishing papers. Thus, tenure-track faculty often do not worry much about teaching.

@@

Successfully mentoring students is a key and most rewarding part of your job as a faculty member. 
There will be times when you feel discouraged and frustrated, but there will also be times when you feel proud and happy.  
For P\&T you will be expected to have successes in mentoring students.  For most good universities, eou will likely need to graduate at least one PhD student to get tenure.
